COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code

### 2021-04-29 2_tables.Rmd
add analysis with country as unit

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", 
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(caption =  "Summary of studies' sampling", linesep = "", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "12em")  %>%
  kableExtra::column_spec(3, width = "30em")
```
## Main Results: Acceptance Rates (disaggregated by group)

@@

>>>>

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", 
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(caption =  "Summary of studies' sampling", linesep = "", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "12em")  %>%
  kableExtra::column_spec(3, width = "30em")
```

## Main Results: Acceptance Rates (disaggregated by group)

@@

## Invariance to aggregation at country level

```{r}
df_country <- 
  df %>% 
  filter(!is.na(take_vaccine_num)) %>%
  filter(!(country %in% c("USA", "Russia"))) %>%
  mutate(cluster_1 = country,
         cluster_2 = recode(country, 
                          "Pakistan 1" = "Pakistan",
                          "Pakistan 2" = "Pakistan",
                          "Sierra Leone 1" = "Sierra Leone",
                          "Sierra Leone 2" = "Sierra Leone",
                          "Uganda 1" = "Uganda",
                          "Uganda 2" = "Uganda",
                          )) %>%
  group_by(country) %>% mutate(weight_1 = weight/sum(weight)) %>% ungroup() %>%
  group_by(cluster_2) %>% mutate(weight_2 = weight_1/sum(weight_1)) %>% ungroup()

# Inspect weights 
df_country %>% group_by(country) %>% summarize(w1 = sum(weight_1), w2 = sum(weight_2)) %>% kable

unit_check <- 
  list(
    study = lm_robust(data = df_country, 
              formula = take_vaccine_num ~ 1, cluster = cluster_1,
              weight = weight_1, se_type = "stata"),

    country = lm_robust(data = df_country, 
              formula = take_vaccine_num ~ 1, cluster = cluster_2,
              weight = weight_2, se_type = "stata")) %>%

  lapply(tidy) %>% bind_rows(.id = "Unit")

unit_check %>% kable(digits = 2)
```
